---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggsegKong

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegKong/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ggsegverse/ggsegKong/actions/workflows/R-CMD-check.yaml)
[![r-universe](https://ggsegverse.r-universe.dev/badges/ggsegKong)](https://ggsegverse.r-universe.dev/ggsegKong)
<!-- badges: end -->

Kong Cortical Parcellation Atlases for the ggsegverse Ecosystem.

## Installation

```{r, eval = FALSE}
# From r-universe
install.packages("ggsegKong", repos = "https://ggsegverse.r-universe.dev")

# From GitHub
# install.packages("remotes")
remotes::install_github("ggsegverse/ggsegKong")
```

## Atlases
### kong2019

Kong 2019 MS-HBM 17-network cortical parcellation.

```{r kong2019}
library(ggsegKong)
plot(kong2019())
```

### kong2022

Kong 2022 Areal MS-HBM 17-network parcellations at 10 resolutions.

| Parcels | Function |
|--------:|:---------|
| 100 | `kong2022_100()` |
| 200 | `kong2022_200()` |
| 300 | `kong2022_300()` |
| 400 | `kong2022_400()` |
| 500 | `kong2022_500()` |
| 600 | `kong2022_600()` |
| 700 | `kong2022_700()` |
| 800 | `kong2022_800()` |
| 900 | `kong2022_900()` |
| 1000 | `kong2022_1000()` |

```{r kong2022_100}
plot(kong2022_100())
```

```{r kong2022_1000}
plot(kong2022_1000())
```
## Data source

Kong 2019: [ThomasYeoLab/CBIG](https://github.com/ThomasYeoLab/CBIG) (MATLAB group priors).
Kong 2022: [ThomasYeoLab/CBIG](https://github.com/ThomasYeoLab/CBIG) (fsaverage5 annotations).

- **References**: Kong et al. (2019) [doi:10.1093/cercor/bhy123](https://doi.org/10.1093/cercor/bhy123); Kong et al. (2022) [doi:10.1093/cercor/bhab101](https://doi.org/10.1093/cercor/bhab101)
- **Date obtained**: 2026-03-28
