---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 10,
  fig.retina = 3
)
```

# ggsegKong

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegKong/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ggsegverse/ggsegKong/actions/workflows/R-CMD-check.yaml)
[![r-universe](https://ggseg.r-universe.dev/badges/ggsegKong)](https://ggseg.r-universe.dev/ggsegKong)
<!-- badges: end -->

Kong cortical parcellation atlases for the ggseg ecosystem. Includes the
Kong 2019 individual-specific parcellation and Kong 2022 multi-resolution
parcellations (100-1000 parcels).

## Installation

We recommend installing the ggseg-atlases through the ggseg
[r-universe](https://ggseg.r-universe.dev/ui#builds):

```{r}
#| label: install-r-universe
#| eval: false
options(
  repos = c(
    ggseg = "https://ggseg.r-universe.dev",
    CRAN = "https://cloud.r-project.org"
  )
)

install.packages("ggsegKong")
```

You can install this package from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("ggsegverse/ggsegKong")
```

## Kong 2019

```{r}
#| label: kong2019
library(ggseg)
library(ggsegKong)
library(ggplot2)

ggplot() +
  geom_brain(
    atlas = kong2019(),
    mapping = aes(fill = label),
    position = position_brain(hemi ~ view),
    show.legend = FALSE
  ) +
  scale_fill_manual(values = kong2019()$palette, na.value = "grey") +
  theme_void()
```

## Kong 2022 

comes in variants of 100 - 1000.

```{r}
#| label: kong2022-400
ggplot() +
  geom_brain(
    atlas = kong2022_400(),
    mapping = aes(fill = label),
    position = position_brain(hemi ~ view),
    show.legend = FALSE
  ) +
  scale_fill_manual(values = kong2022_400()$palette, na.value = "grey") +
  theme_void()
```

## Data source

Kong R, Li J, Orban C, Sabuncu MR, Liu H, Schaefer A, Sun N, Zuo XN,
Holmes AJ, Eickhoff SB, & Yeo BTT (2019). Spatial topography of individual-
specific cortical networks predicts human cognition, personality, and emotion.
*Cerebral Cortex*, 29(6), 2533-2551.

Kong R, Yang Q, Gordon E, et al. (2022). Individual-specific areal-level
parcellations improve functional connectivity prediction of behavior.
*Cerebral Cortex*, 31(10), 4477-4500.
